A Graph Theory Based Approach to MDAO Problem Formulation

### 2013-04-09 graph_syntax.tex
re-wrote objective and constraint section without expression nodes

\subsection{Objectives, and Constraints}
Objectives and constraints are also constructs that need to be identified by engineers 
as part of the design process. In the case of objective functions single output values 
could be selected, but commonly multiple values are assembeled together via simple 
algebraic expression to form a objective function. For example, the problem from 
Fig. \ref{f:designvars} might have an objective function of $z^2$ or $2y + z$. Constraints are 
always given in the form of either an inequality of an equality, e.g. 
$\frac{2y}{10}-1<0$ or $3x+2y - 5=0$. In both cases, an engineer compiles an
algebraic expression that is a function of existing variable nodes in the graph.

For the proposed syntax, objectives and constraints are represented through the use of 
expression nodes. These nodes contain the actual mathematical expression used to define the 
objective or constraint value. Objective or constraint nodes are distinguished
via the presence of a simple expression (objective) vs an inequality/equality (constraint). 
Fig. \ref{f:obj-cons} shows the notional problem graph augmented with objective and 
constraint values.

((DP: I think this definition of objective/constraint is disharmoneous with our other node types. I think it should also have local inputs represented by variables nodes))

>>>>

\subsection{Objectives, and Constraints}
Objectives and constraints are also constructs that need to be identified by engineers 
as part of the design process. In the case of objective functions single output values 
could be selected, but commonly multiple values are assembeled together via simple 
algebraic expression to form a objective function. For example, the problem from 
Fig. \ref{f:designvars} might have an objective function of $z^2$ or $2y + z$. Constraints are 
always given in the form of either an inequality of an equality, e.g. 
$\frac{2y}{10}-1<0$ or $3x+2y - 5=0$. In both cases, an engineer compiles an
algebraic expression that can be evaluated to produce an output.

These operations, though very simple, are effectively the same kind of task 
performed by an analysis block. A constraint or objective function can therfore 
be represented as another analysis block on the graph, with it's own input and 
output variable nodes. Although fundamentally no different than an analysis block, 
for clarity and convience it is useful to distinguish between regular analysis 
blocks and those that arise from the addition of objectives or constraints to 
the graph. So we define an expression block, as the collection of variable and model 
nodes related to a given objective or constraint function. Fig. \ref{f:obj-cons}
shows a notional problem graph augmented with expression blocks and appropriate 
connection edges.
